\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,                % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[hidelinks]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt}

% resume starts here
\begin{document}

% name
\centerline{\Huge Mustafa Sheikh}

\vspace{5pt}

% contact information
\centerline{\href{}{Canadian Citizen} | \href{mailto:mustafa.sheikhj@gmail.com}{mustafa.sheikhj@gmail.com} | \href{wwww.linkedin.com/in/mustafajsheikh}{www.linkedin.com/in/mustafajsheikh} | \href{}{313-782-1205}}

\vspace{-10pt}

% skills section
\section*{Skills}
\textbf{Languages:} Python, C/C++, MATLAB/Simulink, SolidWorks, Julia, UML, LabView \\
\textbf{Tools:} dSPACE Tools, Intrepid Vehicle Spy, Vector CANoe, SAFe, Git, SVN Jira, HIL \\

\vspace{-6.5pt}

% experience section
\section*{Experience}
\textbf{Senior Virtual Hardware Engineer,} \href{}{General Motors} -- Milford, MI\hfill Nov 2022 -- Sept 2024\\
\vspace{-9pt}
\begin{itemize}
  %\item Utilized hardware virtualization to accelerate delivery of software for Software-Defined Vehicle platform.
  \item Championed and secured organizational buy-in for \$2 million Synopsys Virtualizer based 'shift-left' approach to Connectivity Module development enabling exploratory early designs.
  \item Led cross-functional development and delivery of Synopsys Virtualizer based Occupant Safety Module with test software, accelerating integration testing efforts by 4 months ahead of official software availability.
  \item Successfully launched next-generation ASTC Vlab based Central Gateway Module 8 months ahead of hardware schedule, driving concept-to-release progress and facilitating early software testing and integration.
  \item Leveraged expertise in virtual workflows to collaborate with product owners and release train engineers to integrate virtual hardware team into enterprise level agile framework.
  \item Scrum Lead for team of 12 as part SAFe for CAN and Ethernet ECUs for GM’s SDV Platform.
  \item Developed strategy to benchmark virtualization solutions serving as the basis for tool-chain decisions worth \$100k+ .
  \item Utilized Vehicle Spy, CANoe, and WireShark to log and troubleshoot ECUs.
\end{itemize}

\textbf{Senior Connectivity Development Engineer,} \href{}{General Motors} -- Warren, MI \hfill Mar 2021 -- Nov 2022 \\
\vspace{-9pt}
\begin{itemize}
  \item Spearheaded sourcing of Connectivity Module serving as the cornerstone for the Software-Defined Vehicle platform by leading a cross-functional team to select best supplier based on internal metrics.
  \item Led multidisciplinary requirements development meetings for features representing \$10s of millions in business value.
  \item Leveraged agile principles to preempt and resolve issues while keeping leadership apprised for quick updates in strategy.
  \item Helped safeguard \$10s of millions in revenue and critical safety features for hundreds of thousands of OnStar customers impacted by the 2G/3G sunset by developing a mitigation plan with senior leaders.
\end{itemize}

\textbf{Telematics System Integration Lead,} \href{}{Aerotek (Contract at GM)} -- Warren, MI \hfill Sept 2020 -- Mar 2021 \\
\vspace{-9pt}
\begin{itemize}
  \item Led cross-functional workshops between subject matter experts and suppliers to ensure project requirements were met.
  \item Proactively tackled development and implementation challenges in test setups and provided direction for creating electrical testing harnesses while mentoring junior engineers.
  \item Engaged system architects, subject experts, and suppliers to work on OTA related change requests for existing telematics modules to spearhead GM’s evolving OTA strategy.
\end{itemize}

\textbf{Software Controls Engineer,} \href{}{FAW US Research and Development} -- Plymouth, MI \hfill Feb 2020 -- Aug 2020 \\
\vspace{-9pt}
\begin{itemize}
  \item Researched Vehicle Dynamics models and methods of Lateral Control for vehicles under typical highway scenarios in MATLAB/Simulink for ADAS and autonomy.
  \item Independently developed and executed test plans for PID based longitudinal and LQR based lateral control algorithms using MATLAB, allowing team to catch and resolve issues before integration.
  \item Worked closely with integration team to integrate and debug Software Releases in CarMaker SIL environment.
  \item Developed Object Oriented MATLAB scripts to analyze an visualize CAN data from MobilEye EyeQ4 system.
\end{itemize}

\hfill \break
\hfill \break

\textbf{End-of-Line Test Development Engineer,} \href{}{Molex LLC} -- Rochester Hills, MI \hfill Nov 2018 -- Feb 2020 \\
\vspace{-9pt}
\begin{itemize}
  \item Developed multi-threaded Python scripts to flash Firmware on in-vehicle Ethernet Gateway subsystem automating a 60 minute error-prone manual process down to 15 minutes with logs.
  \item Designed and documented manufacturing test solutions using UML methods and engaged in peer-review to verify functionality ensuring first-time quality of solutions in Python and LabView.
  \item Led identification and mitigation of risks in production lines during PFMEA discussions with a global cross-functional team for Ethernet Switch Module subsystems and high-speed cables.
  \item Partnered with senior leaders to address production rework issues, creating timely work instructions that improved reliability and reduced testing time for multiple OEM programs.
\end{itemize}

\textbf{Senior HIL Automation Engineer,} \href{}{Ford Motor Company} -- Dearborn, MI \hfill Apr 2013 -- Nov 2018 \\
\vspace{-9pt}
\begin{itemize}
  \item Drove the integration and extension of Ford Sync automation tool created in Python enabling automated Infotainment testing at scale saving 100s of human hours.
  \item Initiated, designed, and delivered dSPACE license restructuring efforts that freed up \$80k worth of wasted software licenses while also allowing team to scale up from 10 to 40 engineers.
  \item Boosted testing efficiency with a Python-based automated Electronic Latch feature testing fixture, enabling continuous 24/7 remote testing and accelerating product development.
\end{itemize}

\textbf{HIL Engineer,} \href{}{EASi (Contract at Ford)} -- Dearborn, MI \hfill June 2012 -- Apr 2013 \\
\vspace{-9pt}
\begin{itemize}
  \item Led HIL Testing and Automation activities for HIL subsystems by integrating and extending AutomationDesk solutions.
  \item Improved Robotic HMI tester by increasing maintainability and setup time by ~50\% via simplifying data structures.
  \item Slashed HIL part costs by 75\% through BOM management of 3 vehicle platforms, involving 100s of components.
\end{itemize}

\textbf{Intern,} \href{}{Fraunhofer USA} -- Plymouth, MI \hfill Oct 2011 -- Mar 2012 \\
\vspace{-9pt}
\begin{itemize}
  \item Validated and aligned high-power Diode Laser systems.
  \item Supported run-off production assisting engineers in assembly and fixture design.
\end{itemize}

\textbf{Summer Intern,} \href{}{Institute for Imaging Research} -- Windsor, ON \hfill Jun 2011 -- Oct 2011 \\
\vspace{-9pt}
\begin{itemize}
  \item Utilized MATLAB to analyze for performing root-cause analysis and modeling of Ultrasonic sensor noise.
  \item Presented data and conclusions to leadership of the institute at end-of-term.
\end{itemize}

% \textbf{Job Title,} \href{https://www.fstl1992.com/}{Company} -- City, ST \hfill XXXX -- XXXX \\
% \vspace{-9pt}

\vspace{-18.5pt}

% education section
\section*{Education}
\textbf{\href{https://www.uwindsor.ca/}{University of Windsor}} -- BSc in Physics \hfill Oct 2011 \\
\textbf{\href{https://www.uwindsor.ca/}{University of Windsor}} -- BASc in Electrical Engineering \hfill Oct 2009

\end{document}
