%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Mustafa}{Sheikh}{ \urlstyle{same}\url{www.linkedin.com/in/mustafajsheikh} \\
\href{mailto:mustafa.sheikhj@gmail.com}{mustafa.sheikhj@gmail.com} | 313.782.1205
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Summary}

%\location{
Software Tools Developer and \\ Electrical Engineer
with six years \par of professional experience working \par in an agile corporate environment. \\
\\
Skilled at gathering requirements to \par deliver hardware and
software \par solutions for complex problems while \\
collaborating with global teams.\\
%}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     OBHECTIVE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Objective}

%\location{
%Looking for opportunities in \\ Embedded Software field.

%}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
%\location{Adept:}
Shell \textbullet{} Python \textbullet{} MATLAB \\
%\location{Familiar:}
C \textbullet{} C++ \textbullet{} Git \textbullet{} SVN\\
%\location{Familiar:}
%AS3 \textbullet{} iOS \textbullet{} Android \textbullet{} MySQL
\sectionsep

\subsection{Engineering}
%\location{Over 5000 lines:}
Simulink \textbullet{}   Project Management \\
Testing \textbullet{} Fixture Design \\ 
%\location{Over 1000 lines:}
dSPACE Tools \textbullet{} Smart Motor Control \\
LabView
%\location{Familiar:}
%AS3 \textbullet{} iOS \textbullet{} Android \textbullet{} MySQL
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Windsor}
\descript{BSc in Physics}
\location{Oct 2011 | Windsor, ON }
\location{ Cum. GPA: 85\% \\
Major GPA: 88\%}
\sectionsep

\subsection{University of Windsor}
\descript{BSc in Electrical Engineering }
\location{Oct 2009 |Windsor, ON \\ Cum. GPA: 84\%}
Conc. in Communications with Co-op \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Links} 
%Github:// \href{https://github.com/deedydas}{\custombold{deedydas}} \\
%LinkedIn://  \href{https://www.linkedin.com/in/debarghyadas}{\custombold{debarghyadas}} \\
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Physics}
Quantum Mechanics \\
Statistical Mechanics \\
Classical Mechanics \\
Electromagnetism \\
Fourier Analysis \\
Complex Analysis \\
%Compilers + Practicum \\
%Cloud Computing \\
\sectionsep

\subsection{Engineering}
Coding and Information Theory \\
%Image and Video Processing\\
Digital Signal Processing \\
Multimedia Systems \\
Control Systems Engineering \\
Wireless Communication \\
%Functional Programming \\
%Computer Graphics + Practicum \\
%{\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst) }}} \\
%Unix Tools and Scripting \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Molex Connected Mobility}
\descript{| Software Development Engineer}
\location{January 2019 – Present | Rochester Hills, MI}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed and delivered Python based multi-threaded solution to flash software on multiple Automotive Ethernet Gateway module subsystem in vehicle using a web-interface for OEM and subsidiary which is currently being used production and testing purposes. 
	\begin{tightemize}
	\vspace{\topsep} % Hacky fix for awkward extra vertical space
	\item The solution optimized and automated a very tedious manual process which was error prone took decreased time to flash from ~ 60 min per vehicle to ~20 min.
	\item Initial solution was continually improved and is planned to be sold to OEM as part of new Firmware releases.
	\vspace{\topsep} % Hacky fix for awkward extra vertical space
	\end{tightemize}
\item Worked on-site on Autonomous Vehicles to support OEM engineers and Ethernet Gateway firmware engineers to support testing and debugging. 
\item Investigated and advised on best practices for LabView and it's use for in-house production testing solutions.
\item Lead production testing efforts to review PFMEA as part of a cross-functional team.
\end{tightemize}
\sectionsep

\runsubsection{Ford Motor Company}
\descript{| Lead Feature Expert }
\location{July 2018 – Decmber 2018| Allen Park, MI}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Responsible for testing of Cross Traffic Alert Feature for new vehicles.
\item Defined HW boundary and scope of testing while leading off-shore resources to ensure proper testing was completed within scope.
\end{tightemize}
\sectionsep

\runsubsection{Ford Motor Company}
\descript{| Automation Solutions Developer }
\location{January 2015 – June 2018 | Dearborn, MI}
\begin{tightemize}
\item Created tool to facilitate manual testing for HIL racks used by +40 people in Python using dSPACE API: increasing efficiency and user productivity.
\item Researched and proto-typed Appium based Phone Automation solution in Python which was later developed as a full fledged solution by junior engineer who I mentored.
\item Adapted, integrated, extended, and maintained Squish based Sync touchscreen automation tool created in Python. Enabled our lab to perform automated testing for features with Sync screen.
\item Worked with internal customers and external suppliers to develop and deliver automated locking solution which required Python and part design expertise.
\end{tightemize}
\sectionsep

\runsubsection{Ford Motor Company}
\descript{| HIL Engineer}
\location{June 2012 – December 2014 | Dearborn, MI}
\begin{tightemize}
\item Successfully restructured and deployed dSPACE license scheme to maximize usage and minimize cost by bundling license dongles by user function.
\item Managed and acquired licenses for the group of +40 people with an operating budget of ~125k USD per annum and total value of ~1 million USD.
%\item Lead for global communication group which consisted of with teams from Germany, India, China, Mexico, and Australia
\item Successfully performed parts acquisition and BOM validation for 100s of parts for 3 HIL racks for two separate programs simultaneously. 
\item Worked with suppliers, engineers, and Ford purchasers to resolve issues and negotiate timelines and deliverables.
\item Lead for Powertrain HIL Subsystem which required coordinating changes and expanding capability using MATLAB and Simulink for modelling or reading schematics to make hardware changes.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Awards} 
%\begin{tabular}{rll}
%2014	     & top 52/2500  & KPCB Engineering Fellow\\
%2014	     & 2\textsuperscript{nd} most points  & Google Code Jam, Qualification Round\\
%2014	     & 1\textsuperscript{st}/50  & Microsoft Coding Competition, Cornell\\
%2013	     & National  & Jump Trading Challenge Finalist\\
%2013     & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament  \\
%2012     & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
%2011     & National & Indian National Mathematics Olympiad (INMO) Finalist \\
%2010     & National & Comp. Soc. of India's National Programming Contest\\
%\end{tabular}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Societies} 

%\begin{tabular}{rll}
%2014 	& top 12\%ile    & Tau Beta Pi Engineering Honor Society\\
%2014   & National   & The Global Leadership and Education Forum (tGELF)\\
%2012   &  National  & Golden Key International Honor Society\\
%2012   &  National   & National Society of Collegiate Scholars\\
%\end{tabular}
%\sectionsep

\end{minipage} 
\end{document}  
\documentclass[]{article}
